Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-10-11 manuscript/paper-tycho.tex
Tycho/SN1006 resolution errs, run B-damp tables
Check errors on single e- synchrotron emissivity table (fglists.dat),
e- distribution integrals, etc. New single e- table (fglists_mod.dat),
change several computation resolutions.
Change Tycho e- spectrum index.
Modify B-damping table set-up, start running.

% TODO Come back after checking Pacholczyk resolution
As the full model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals (discretization over
radial coordinate, line-of-sight coordinate, electron distribution, Green's
function integrals).  We chose our integration resolutions such that the
fractional error in model FWHMs associated with halving/doubling integration
resolution is less than $1\%$ for the parameter space relevant to our
filaments.

>>>>

As the full model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals (discretization over
radial coordinate, line-of-sight coordinate, electron distribution, Green's
function integrals).  We chose integration resolutions such that the
fractional error in model FWHMs associated with halving or doubling integration
resolution is less than $1\%$ for the parameter space relevant to our
filaments (up to $\eta_2 = 10^3$ for loss-limited model; up to $\eta_2 = 10$
for magnetic damping model).  In our error analysis, the maximum resolution
errors in a small sample of parameter space are typically $0.1$--$1\%$,
but mean and median errors are typically an order of magnitude smaller.
